Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-03 paper/paper.tex

The values of $m(x)$ are in this work derived from the SEAM Overthrust
model~\cite{aminzadeh1996three} over a grid of $287 \times 881 \times 881$
points, including an absorbing layer of 40 points on each side. The grid spacing
is 25m in space and TODO in time. This is run for 2500 timesteps. The wave field
at the final time is shown in Figure~\ref{fig:uncompressed}, and only this field
was used for the compression experiments in this paper.

>>>>

The values of $m(x)$ used in this work are derived from the SEAM Overthrust
model~\cite{aminzadeh1996three} over a grid of $287 \times 881 \times 881$
points, including an absorbing layer of 40 points on each side. The grid spacing
is 25m in space. This is run for 2500 timesteps. The wave field
at the final time is shown in Figure~\ref{fig:uncompressed}, and only this field
was used for the compression experiments in this paper. The uncompressed size of
this single time step field is just under 900MB.
